% \documentclass[useAMS, usenatbib, preprint, 12pt]{aastex}
\documentclass[useAMS, usenatbib]{mn2e}
\usepackage{cite, natbib}
\usepackage{float}
\usepackage{epsfig}
\usepackage{cases}
\usepackage[section]{placeins}
\usepackage{graphicx, subfigure}
\usepackage{color}
\usepackage{bm}

\newcommand{\naigrain}{333}
\newcommand{\nmcquillan}{100}
\newcommand{\kepexample}{1430163}
\newcommand{\kepexampleperiod}{4}
\newcommand{\aigrainexampleperiod}{20.8}
\newcommand{\Kepler}{{\it Kepler}}
\newcommand{\kepler}{\Kepler}
\newcommand{\corot}{{\it CoRoT}}
\newcommand{\Ktwo}{{\it K2}}
\newcommand{\ktwo}{\Ktwo}
\newcommand{\TESS}{{\it TESS}}
\newcommand{\tess}{{\it TESS}}
\newcommand{\LSST}{{\it LSST}}
\newcommand{\Wfirst}{{\it Wfirst}}
\newcommand{\SDSS}{{\it SDSS}}
\newcommand{\PLATO}{{\it PLATO}}
\newcommand{\Gaia}{{\it Gaia}}
\newcommand{\gaia}{{\it Gaia}}
\newcommand{\Teff}{$T_{\mathrm{eff}}$}
\newcommand{\teff}{$T_{\mathrm{eff}}$}
\newcommand{\FeH}{[Fe/H]}
\newcommand{\feh}{[Fe/H]}
\newcommand{\ie}{{\it i.e.}}
\newcommand{\eg}{{\it e.g.}}
\newcommand{\logg}{log \emph{g}}
\newcommand{\dnu}{$\Delta \nu$}
\newcommand{\numax}{$\nu_{\mathrm{max}}$}
\newcommand{\acfRMS}{9.27}
\newcommand{\pgramRMS}{1.25}
\newcommand{\mcmcRMS}{0.46}
\newcommand{\racomment}[1]{{\color{blue}#1}}

\newcommand{\columbia}{1}
\newcommand{\simons}{2}
\newcommand{\pton}{3}
\newcommand{\nyu}{3}
\newcommand{\cca}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\uw}{7}

\begin{document}

\title{Testing gyrochronology with Gaia comoving pairs}

\author[R.~Angus \emph{et al.}]{%
    Ruth~Angus,$^1$\thanks{ruth.angus@astro.ox.ac.uk}
    Semyeong Oh$^2$
    Adrian Price-Whelan$^2$
    David W. Hogg$^{3, 4, 5, 6}$
    Daniel Foreman-Mackey$^4$
    Matt Wilde$^7$ \\
    $^1$Columbia University, Simons Fellow
    $^2$Princeton University
    $^3$NYU
    $^4$CCA
    $^5$MPIA
    $^6$CDS
    $^7$UW}

% \author{%
%     Ruth Angus\altaffilmark{\columbia, }\altaffilmark{\simons},
%     Semyeong Oh\altaffilmark{\pton},
%     Adrian Price-Whelan\altaffilmark{\pton},
%     David W. Hogg\altaffilmark{\nyu, }\altaffilmark{\cca, }
%     \altaffilmark{\mpia, }\altaffilmark{\cds},
%     Daniel Foreman-Mackey\altaffilmark{\cca, }\altaffilmark{\uw},
%     Matt Wilde\altaffilmark{\uw},
%     Stephanie Douglas\altaffilmark{\columbia},
%     David Kipping\altaffilmark{\columbia},
%     Marcel Agueros\altaffilmark{\columbia} \&
%     David Spergel\altaffilmark{\pton, }\altaffilmark{\cca}
% }

% \altaffiltext{\columbia}{Department of Astronomy, Columbia
% University, NY, NY}
% \altaffiltext{\simons}{Simons Fellow, RuthAngus@gmail.com}
% \altaffiltext{\nyu}{Center for Cosmology and Particle Physics, New York
% University, NY, NY}
% \altaffiltext{\cca}{Center for Computational Astrophysics, Flatiron Institute,
% NY, NY}
% \altaffiltext{\mpia}{Max Planck Institute of Astronomy, Heidelberg, Germany}
% \altaffiltext{\cds}{Center for Data Science, New York University, NY, NY}
% \altaffiltext{\pton}{Princeton University}
% \altaffiltext{\uw}{University of Washington}

\begin{abstract}
    The rotation periods of main sequence, FGK stars increase over time and can
    be used to infer their ages via gyrochronology.
    However, the precision and accuracy of the gyrochronology method over has
    not yet been established over a large range of masses and ages, in part
    because young cluster stars provide the majority of calibrators.
    Trends observed in young clusters are usually extrapolated to older field
    stars.
    Widely separated binaries provide an intermediate step between clusters
    and the field.
    The Tycho-Gaia Astrometric Solution (TGAS) catalog published in Gaia DR1
    revealed thousands of previously unknown comoving pairs and groups of
    stars. Several hundred of these stars fall in the Kepler field and
    have precise light curves covering several rotational cycles. We use the
    rotation periods of these comoving stars to quantify the effectiveness of
    gyrochronology at a range of ages and masses. Although this is not the
    first study of gyrochronology with binary stars, most gyrochronology
    studies have been performed with open clusters or, more recently, with
    asteroseismic field stars. Recent studies show evidence for a departure
    from classical gyrochronology models for old-age field stars, which has
    not been observed in clusters. Binaries and comoving stars, particularly
    at large separations, bridge the gap between clusters and the field. In
    addition, the incredible astrometric precision of Gaia, combined with the
    radial velocities we obtained for a large fraction of these stars in order
    to validate their comoving status, provides a large number of extremely
    high fidelity comoving stars, an excellent test sample for gyrochronology.

    \racomment{Can we constrain the precision of gyrochronology from these
    binaries when we don't know how they formed?  What can we actually say?
    Can we use the precision inferred from clusters to extrapolate to the
    binaries and draw conclusions about how many of these clusters formed
    together?
    Either way, I will need to know the precision of gyrochronology in
    clusters.}
\end{abstract}

\include{intro}

\include{data}

\include{method}

\racomment{Could demonstrate the reliability of gyrochronology alongside
isochrone fitting.
(See https://arxiv.org/pdf/1801.00537.pdf)

Also, use the groups.}


\include{discussion}

\include{conclusion}

% acknowledgements
This research was funded by the Simons Foundation.
This work is based on observations obtained at the MDM Observatory, operated
by Dartmouth College, Columbia University, Ohio State University, Ohio
University, and the University of Michigan.
Some of the data presented in this paper were obtained from the Mikulski
Archive for Space Telescopes (MAST).
STScI is operated by the Association of Universities for Research in
Astronomy, Inc., under NASA contract NAS5-26555.
Support for MAST for non-HST data is provided by the NASA Office of Space
Science via grant NNX09AF08G and by other grants and contracts.
This paper includes data collected by the Kepler mission. Funding for the
Kepler mission is provided by the NASA Science Mission directorate.

\end{document}

% \bibliographystyle{plainnat}
% \bibliography{teacups}
% \end{document}
